### 2014-02-23 paper/retrofit.tex
More typing rules.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Start of an erasure function.

\begin{figure}
\begin{mathpar}

\end{mathpar}

\caption{Typing rules for ML-like language}
\label{fig:ml-typing}
\end{figure}

@@

>>>>

\begin{figure}
\begin{mathpar}
\inferrule[T-ty-address]
{}
{| tyrule tG tS a (ref (tyLookup tS a)) |}
\end{mathpar}

\caption{Selected typing rules for ML-like language}
\label{fig:ml-typing}
\end{figure}

@@

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) = iconf iS its| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    |tconf id il' bullet| & |il' cantFlowTo il| \\
    |tconf id il' (erase ie)| & \text{otherwise}
  \end{cases}
\end{align*}
\caption{Erasure function.}
\end{figure}
